---
title:
output: pdf_document
classoption: landscape
latex_engine: lualatex
# header-includes:
#   - \usepackage{draftwatermark}
params:
  text: ""
  iso_alpha_3_code: ""
  who_name: ""
  round_name_profile: ""
  years: ""
  df: ""
  df_excluded: ""
  estimates: ""
  estimates_arr: ""
  meta: ""
  table1_years: ""
  lang: ""
---
# `r params$text$"main title"` `r params$who_name` `r params$years`

## `r params$text$"main title 2"`

```{r setup, include=FALSE, results='hide',message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
library(kableExtra)
library(float)
align_headers <- "l"
```


<!-- page 1 -->
```{r echo=FALSE ,message=FALSE, warning=FALSE}
# TABLE 1 ESTIMATES PAGE 1


tbl1 <- estimates %>%
  dplyr::ungroup() %>%
  dplyr::rename(low = `0.1`,
                mid = `0.5`,
                up = `0.9`) %>%
  dplyr::select(year_mid, parameter, low, mid, up) %>%
  tidyr::pivot_wider(
    names_from = parameter,
    values_from = c(low, mid, up)
  ) %>%
  dplyr::mutate_at(c("mid_mmr", "low_mmr", "up_mmr"), round) %>%
  dplyr::mutate_at(c("mid_pm", "low_pm", "up_pm"), round, 2) %>%
  dplyr::mutate(mmr = paste0(mid_mmr,' [', 	low_mmr,', ',	up_mmr, ']'),
                pm = paste0(mid_pm,' [', 	low_pm,', ',	up_pm, ']')) %>%
  dplyr::mutate(
                births = round(mid_births/1000),
                maternal = round(mid_maternal_deaths),
                hiv = round(mid_hiv_related_indirect_maternal_deaths)) %>%
  dplyr::select(year = year_mid,
                mmr,
                maternal,
                hiv,
                births,
                pm) %>%
  dplyr::relocate(year, mmr, pm, hiv, births) %>%
  dplyr::filter(year %in% table1_years)

a <- params$text$"table 1 referenec a"
b <- params$text$"table 1 reference b"
c <- params$text$"reference live births"
d <- params$text$"reference mortality"
sym1 <- params$text$"table 1 symbol 1"
sym2 <- params$text$"table 1 symbol 2"
sym_period <- params$text$"period endpoints statement"
extra <- NULL
if(iso_alpha_3_code == "SRB") {
extra <- "Data for Serbia do not include data for Kosovo (United Nations Security Council Resolution 1244 (1999))"
}

if(iso_alpha_3_code == "LUX") {
extra <- "All cause deaths to women 15-49 for Luxembourg are obtained from WHO Mortality Database"
}

  # "Periods use interval notation where [a,b) describes an interval greater than or equal to a and less than b and [a,b] describes an interval greater than or equal to a and less than or equal to b"
kableExtra::kbl(tbl1,
                booktabs = T,
                align = align_headers,
                caption = params$text$"table 1 title",
                escape = F,
                col.names = kableExtra::linebreak(c(
                              paste0(params$text$"table 1 column names 1"),
                              paste0(
                                params$text$"table 1 column names 2", kableExtra::footnote_marker_alphabet(1), kableExtra::footnote_marker_symbol(1), kableExtra::footnote_marker_symbol(2)
                                ),
                              paste0(
                                params$text$"table 1 column names 3",kableExtra::footnote_marker_alphabet(2), kableExtra::footnote_marker_symbol(1), kableExtra::footnote_marker_symbol(2)
                                ),
                              paste0(
                                params$text$"table 1 column names 4",kableExtra::footnote_marker_symbol(2)
                                ),
                              paste0(
                                params$text$"table 1 column names 5",kableExtra::footnote_marker_alphabet(3),
                                "\n ",
                                params$text$"table 1 column names 5 denominator"),
                              paste0(
                                params$text$"table 1 column names 6", kableExtra::footnote_marker_symbol(2)
                                )
                              ),
                              align = align_headers
                              )
                ) %>%
  # kable_styling(full_width = T) %>%
  kableExtra::kable_styling(latex_options = c("striped", "HOLD_position"))  %>%
  kableExtra::footnote(symbol = c(sym1, sym2, extra),
                       alphabet = c(a,b,c),
                        escape = FALSE,
                       threeparttable = T)

```


\newpage
<!-- page 2  estimates arr and change -->
```{r echo=FALSE ,message=FALSE, warning=FALSE}
sym2 <- params$text$"table 1 symbol 2"

estimates_arr <- estimates_arr %>%
  dplyr::ungroup() %>%
  dplyr::select(-iso_alpha_3_code) %>%
  dplyr::rename(low = `0.1`,
                mid = `0.5`,
                up = `0.9`) %>%
  dplyr::mutate_at(c("low", "mid", "up"), round, 2) %>%
  dplyr::mutate(value = paste0(mid," [",low,", ", up,"]")) %>%
  dplyr::select(period, parameter, value) %>%
  tidyr::pivot_wider(names_from = parameter, values_from = value)
kableExtra::kbl(estimates_arr,
                booktabs = T,
                align = align_headers,
                escape = F,
                caption = "Annual Rate of Reduction",
                col.names = c(
                              params$text$"table 2 column names 1",
                              paste0(params$text$"table 2 column names 2",kableExtra::footnote_marker_symbol(1)),
                              paste0(params$text$"table 2 column names 3", kableExtra::footnote_marker_symbol(1, double_escape = FALSE))
                )
                ) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "striped", "HOLD_position"))  %>%
  kableExtra::footnote(symbol = c(sym2),
                        escape = FALSE,
                       threeparttable = T) %>%
  kableExtra::column_spec(1, width = "1.25in") %>%
  kableExtra::column_spec(2:3, width = "3in") 
```


\newpage
# `r params$text$"table 3 title"`
<!-- page 3  vr data -->
```{r echo=FALSE ,message=FALSE, warning=FALSE}
tbl3 <- df %>%
  dplyr::filter(type == 'vr') %>%
  dplyr::filter(include) %>%
  dplyr::select(maternal_deaths = obs_matdeaths,
                female_deaths = obs_env,
                adjustment = multiplier,
                sens,
                spec,
                completeness = rho_bmat,
                usability_percentage,
                period,
                include) %>%
  dplyr::mutate(
    maternal_deaths_excluded = ifelse(!include, maternal_deaths, NA),
    maternal_deaths = ifelse(include, maternal_deaths, NA),
    completeness = round(completeness*100, 2),
    sens=round(sens*100, 2), 
    spec=round(spec*100, 2),
    usability_percentage= round(usability_percentage*100, 2),
    adjustment= round(adjustment, 2)
  ) %>%
  dplyr::select(-include) %>%
  dplyr::relocate(period,
                  maternal_deaths,
                  female_deaths) %>%
  dplyr::arrange(period)



a <- params$text$"icd statement"
b <- params$text$"table 3 reference b"
c <- params$text$"table 3 reference c"
d <- params$text$"table 3 reference d"
e <- params$text$"table 3 reference e"
f <- params$text$"table 3 reference f"
g <- params$text$"table 3 reference g"
h <- params$text$"table 3 reference h"
sym2 <- params$text$"reference crvs adjustment"

if(nrow(tbl3) > 0) {
kableExtra::kbl(tbl3,
                format='latex',
                booktabs = T,
                                align = align_headers,
                caption = params$text$"table 3 title",
                col.names = c(paste0(params$text$"table 3 column names 1", kableExtra::footnote_marker_symbol(1)),
                              paste0(params$text$"table 3 column names 2",kableExtra::footnote_marker_alphabet(1)),
                              paste0(params$text$"table 3 column names 3",kableExtra::footnote_marker_alphabet(2)),
                              paste0(params$text$"table 3 column names 4",kableExtra::footnote_marker_alphabet(3), kableExtra::footnote_marker_symbol(2)),
                              paste0(params$text$"table 3 column names 5",kableExtra::footnote_marker_alphabet(4), kableExtra::footnote_marker_symbol(2)),
                              paste0(params$text$"table 3 column names 6",kableExtra::footnote_marker_alphabet(5), kableExtra::footnote_marker_symbol(2)),
                              paste0(params$text$"table 3 column names 7",kableExtra::footnote_marker_alphabet(6), kableExtra::footnote_marker_symbol(2)),
                              paste0(params$text$"table 3 column names 8",kableExtra::footnote_marker_alphabet(7)),
                              paste0(params$text$"table 3 column names 9",kableExtra::footnote_marker_alphabet(8))
                                ),
                escape = FALSE,
                row.names = FALSE,
                longtable = T) %>%
  kableExtra::kable_styling(latex_options = c("scale_down","striped", "HOLD_position", "repeat_header"),
                            font_size = 7) %>%
  kableExtra::footnote(symbol = c(sym_period, sym2), alphabet = c(a,b,c,d,e,f,g,h), escape = FALSE, threeparttable = T)  %>%
  kableExtra::column_spec(1:9, width = ".72in")
} 

```
`r if(nrow(tbl3) == 0 & lang == "English"){"No data available"}`
`r if(nrow(tbl3) == 0 & lang == "Spanish"){"Datos no disponibles"}`
`r if(nrow(tbl3) == 0 & lang == "French"){"Pas de données disponibles"}`

<!-- vr excluded -->
\newpage
# `r params$text$"table 4 title"`
```{r echo=FALSE ,message=FALSE, warning=FALSE}
tbl_vr_ex <- df_excluded %>%
  dplyr::filter(type == 'vr') %>% #might need to exclude other types shown in other sections
  dplyr::filter(!include) %>%
  dplyr::select(completeness = rho_bmat,
                usability_percentage,
                period,
                include_reason) %>%
  dplyr::mutate(
    completeness = round(completeness*100,2),
    usability_percentage = round(usability_percentage*100, 2)
  ) %>%
  dplyr::relocate(period) %>%
  dplyr::arrange(period)

tbl_vr_ex <- tbl_vr_ex %>%
  dplyr::mutate(include_reason = ifelse(include_reason == "usability less than 60%", "Usability < 60\\%",
                                  ifelse(include_reason == "CRVS overlaps with spec. study", params$text$"table 4 reason for exclusion values 1",
                                        ifelse(include_reason == "Quality of census measurement not clear", params$text$"table 4 reason for exclusion values 2",
                                               ifelse(include_reason == "PM could not be obtained", params$text$"table 4 reason for exclusion values 3",
                                                       ifelse(include_reason == "Start date before 1985", params$text$"table 4 reason for exclusion values 4",
                                                              ifelse(include_reason == "Study not nationally representative", params$text$"table 4 reason for exclusion values 5",
                                                                     ifelse(include_reason == "End after last year in estimates", params$text$"table 4 reason for exclusion values 6",
                       ifelse(include_reason == "CRVS completeness <0.95 in a COVID-19 year", params$text$"table 4 reason for exclusion values 8",                                                     
                                                                            include_reason)))))))))

if (nrow(tbl_vr_ex) > 0) {
kableExtra::kbl(tbl_vr_ex,
                booktabs = T,
                                align = align_headers,
                caption = params$text$"table 4 title",
                col.names = c(paste0(params$text$"table 4 column names 1", kableExtra::footnote_marker_symbol(1)),
                              paste0(params$text$"table 4 column names 2",kableExtra::footnote_marker_alphabet(1)),
                              paste0(params$text$"table 4 column names 3",kableExtra::footnote_marker_alphabet(2)),
                              params$text$"table 4 column names 4"
                                ),
                escape = FALSE,
                row.names = FALSE,
                longtable = T
                ) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "striped", "HOLD_position", "repeat_header"))  %>%
  kableExtra::footnote(symbol = c(sym_period), alphabet = c(f,g), escape = FALSE, threeparttable = T)

}
```
`r if(nrow(tbl_vr_ex) == 0 & lang == "English"){"No data excluded"}`
`r if(nrow(tbl_vr_ex) == 0 & lang == "Spanish"){"No datos excluidos"}`
`r if(nrow(tbl_vr_ex) == 0 & lang == "French"){"Aucune donnée exclue"}`


<!-- other data -->
\newpage
# `r params$text$"table 5 title"`
```{r echo=FALSE ,message=FALSE, warning=FALSE, error=TRUE}
# Pregnancy related deathso #do we even have this for any country? its not in the data output or main_data df$definition
#we have definition == 'pregn' and final_pm but no envelope to calculate deaths from this
#ita footnote
extra_ITA_note <- NULL
if (iso_alpha_3_code == "ITA") {
  extra_ITA_note <- "For further information on the ItOSS methodology see: Donati S, Maraschini A, Lega I, D'Aloja P, Buoncristiano M, Manno V, et al. Maternal mortality in Italy: Results and perspectives of record-linkage analysis. Acta Obstet Gynecol Scand 2018 Nov; 97(11):1317-1324"
}
tbl5 <- df %>%
  dplyr::filter(type != 'vr') %>% #might need to exclude other types shown in other sections
  dplyr::filter(include) %>%
  dplyr::mutate(maternal_deaths = ifelse(type=="inq", env_mat, env_mat_final)) %>% 
  dplyr::select(maternal_deaths,
                female_deaths = obs_env,
                final_pm,
                mmr_adjusted = mmr.adj.postmod,
                mmr = final_mmr, #final_mmr_before_crisis,
                definition,
                source = citation_short,
                period,
                source_type = type,
                fp,
                fn,
                up) %>%
  dplyr::mutate(
    mmr_adjusted = mmr_adjusted,
                mmr = mmr,
    pregnancy_related_deaths = NA,
    maternal_pm = ifelse(definition == 'maternal', round(final_pm, 4), NA),
    pregn_pm = ifelse(definition == 'pregn', round(final_pm, 4), NA),
    mmr_adjusted = round(mmr_adjusted*100000, 2),
    mmr = round(mmr*100000, 2)
  )  %>%
    dplyr::mutate(source_type = ifelse(source_type == "inq", "Specialized study",
                                ifelse(source_type == "vr", "CRVS",
                                       ifelse(source_type == "misc", "Miscellaneous",
                                              ifelse(source_type == "dhs", "Survey",
                                                                 ifelse(source_type == "census", "Census", source_type)))))) %>%
  dplyr::select(-final_pm, -definition) %>%
  dplyr::relocate(period,
                  source,
                  source_type,
                  maternal_deaths,
                  pregnancy_related_deaths,
                  female_deaths,
                  maternal_pm,
                  pregn_pm,
                  mmr,
                  mmr_adjusted) %>%
  dplyr::arrange(period)
if (iso_alpha_3_code == "IND") {
  tbl5 <- tbl5 %>%
    dplyr::mutate(maternal_deaths = ifelse(source_type == "Specialized study", NA, maternal_deaths))
}

tbl5 <- tbl5 %>%
  dplyr::mutate(source_type = ifelse(source_type == "Specialized study", params$text$"table 5 source type 1",
                                     ifelse(source_type == "Census", params$text$"table 5 source type 2",
                                            ifelse(source_type == "Survey", params$text$"table 5 source type 3",
                                                   ifelse(source_type == "Miscellaneous", params$text$"table 5 source type 4",
                                                           ifelse(source_type == "CRVS", params$text$"table 5 source type 5", source_type))))))

# This hack hides maternal deaths for IND spec. studies per request by JC



a <- params$text$"table 5 reference a"
b <- params$text$"table 5 reference b"
c <- params$text$"table 5 reference c"
d <- params$text$"table 5 reference d"
#hacked to go in alph order, change to the object letter in the spreadhsheet eventually i.e. next one should have cell renamed to ref f etc
f <- params$text$"table 5 reference e"
g <- params$text$"table 5 reference f"
h <- params$text$"table 5 reference g"
e <- params$text$"table 5 reference h"
sym1 <- params$text$"table 5 symbol 1"
sym2 <- params$text$"table 5 symbol 2"
if (nrow(tbl5) > 0) {
kableExtra::kbl(tbl5,
                booktabs = T,
                align = align_headers,
                caption = params$text$"table 5 title",
                col.names = kableExtra::linebreak(c(
                              paste0(params$text$"table 5 column names 1", kableExtra::footnote_marker_symbol(1)),
                              params$text$"table 5 column names 2",
                              params$text$"table 5 column names 3",
                              paste0(params$text$"table 5 column names 4", kableExtra::footnote_marker_alphabet(1)),
                              paste0(params$text$"table 5 column names 5",kableExtra::footnote_marker_alphabet(2)),
                              params$text$"table 5 column names 6",
                              paste0(params$text$"table 5 column names 7",kableExtra::footnote_marker_alphabet(3)),
                              paste0(params$text$"table 5 column names 8",kableExtra::footnote_marker_alphabet(4), kableExtra::footnote_marker_symbol(3)),
                              paste0(params$text$"table 5 column names 9", kableExtra::footnote_marker_alphabet(5)),
                              paste0(params$text$"table 5 column names 10"),
                              paste0("F+",kableExtra::footnote_marker_alphabet(6), kableExtra::footnote_marker_symbol(2)),
                              paste0("F-",kableExtra::footnote_marker_alphabet(7), kableExtra::footnote_marker_symbol(2)),
                              paste0("U+",kableExtra::footnote_marker_alphabet(8), kableExtra::footnote_marker_symbol(2))
                ),
                align = align_headers),
                escape = FALSE,
                row.names = FALSE,
                longtable = T) %>%
  kableExtra::kable_styling() %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "striped", "HOLD_position", "repeat_header"),
                            font_size = 7) %>%
  kableExtra::footnote(symbol = c(sym_period, sym1, sym2, extra_ITA_note), alphabet = c(a,b,c,d,e,f,g,h), escape = FALSE, threeparttable = T) %>%
  kableExtra::column_spec(1, width = ".7in") %>%
  kableExtra::column_spec(2, width = ".9in") %>%
  kableExtra::column_spec(3, width = ".9in") %>%
  kableExtra::column_spec(4:8, width = ".5in") %>%
  kableExtra::column_spec(9:10, width = ".8in") %>%
  kableExtra::column_spec(11:13, width = ".22in") 
} 
```
`r if(nrow(tbl5) == 0 & lang == "English"){"No data available"}`
`r if(nrow(tbl5) == 0 & lang == "Spanish"){"Datos no disponibles"}`
`r if(nrow(tbl5) == 0 & lang == "French"){"Pas de données disponibles"}`

<!-- other data excluded -->
\newpage
# `r params$text$"table 6 title"`
```{r echo=FALSE ,message=FALSE, warning=FALSE}
tbl6 <- df_excluded %>%
  dplyr::filter(type != 'vr',
                !include) %>% #might need to exclude other types shown in other sections
  dplyr::select(include,
                include_reason,
                source = citation_short,
                source_type = type,
                period) %>%
  dplyr::select(-include) %>%
  dplyr::mutate(source_type = ifelse(source_type == "inq", "Specialized study",
                                ifelse(source_type == "vr", "CRVS",
                                       ifelse(source_type == "misc", "Miscellaneous",
                                              ifelse(source_type == "dhs", "Survey",
                                                     ifelse(source_type == "census", "Census",
                                                          source_type))))))

tbl6 <- tbl6 %>%
  dplyr::mutate(source_type = ifelse(source_type == "Specialized study", params$text$"table 5 source type 1",
                                     ifelse(source_type == "Census", params$text$"table 5 source type 2",
                                            ifelse(source_type == "Survey", params$text$"table 5 source type 3",
                                                   ifelse(source_type == "Miscellaneous", params$text$"table 5 source type 4",
                                                           ifelse(source_type == "CRVS", params$text$"table 5 source type 5", source_type))))))
tbl6 <- tbl6 %>%
  dplyr::mutate(include_reason = ifelse(include_reason == "CRVS overlaps with spec. study", params$text$"table 4 reason for exclusion values 1",
                                        ifelse(include_reason == "Quality of census measurement not clear", params$text$"table 4 reason for exclusion values 2",
                                               ifelse(include_reason == "PM could not be obtained", params$text$"table 4 reason for exclusion values 3",
                                                       ifelse(include_reason == "Start date before 1985", params$text$"table 4 reason for exclusion values 4",
                                                              ifelse(include_reason == "Study not nationally representative", params$text$"table 4 reason for exclusion values 5",
                                                                     ifelse(include_reason == "End after last year in estimates", params$text$"table 4 reason for exclusion values 6",
                                                                            ifelse(include_reason == "No information on maternal deaths", params$text$"table 4 reason for exclusion values 7",
                                                                                    ifelse(include_reason == "CRVS completeness <0.95 in a COVID-19 year", params$text$"table 4 reason for exclusion values 8",
                                                                                  include_reason)))))))))

tbl6 <- tbl6 %>%
  dplyr::relocate(period,
                  source,
                  source_type,
                  include_reason) %>%
  dplyr::arrange(period)

if (nrow(tbl6) > 0) {
kableExtra::kbl(tbl6,
                row.names = FALSE,
                booktabs = T,
                escape = FALSE,
                                align = align_headers,
                caption = params$text$"table 6 title",
                col.names = c(paste0(params$text$"table 6 column names 1", kableExtra::footnote_marker_symbol(1)),
                              params$text$"table 6 column names 2",
                              params$text$"table 6 column names 3",
                              params$text$"table 6 column names 4"
                ),
               
                longtable = T) %>%
  kableExtra::kable_styling() %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "striped", "HOLD_position", "repeat_header")) %>%
  kableExtra::footnote(symbol = c(sym_period), escape = FALSE, threeparttable = T) %>%
  kableExtra::column_spec(1, width = "1in") %>%
  kableExtra::column_spec(2, width = "3in") 
}
```
`r if(nrow(tbl6) == 0 & lang == "English"){"No data excluded"}`
`r if(nrow(tbl6) == 0 & lang == "Spanish"){"No datos excluidos"}`
`r if(nrow(tbl6) == 0 & lang == "French"){"Aucune donnée exclue"}`

\newpage
<!-- predictor table -->
# `r params$text$"table 7 title"`
```{r echo=FALSE ,message=FALSE, warning=FALSE}
tbl_preds <- tibble::tibble(
  year = meta$year.t %>% as.vector(),
  gdp = round(exp(meta$logGDP.ct) %>% as.vector()),
  gfr = round(meta$gfr.ct %>% as.vector() * 1000),
  sab = round(meta$sab.ct %>% as.vector() * 100)
) %>%
  dplyr::filter(year %in% table1_years) %>%
  as.data.frame()


star <- params$text$"gdp 2" #states that gdp is smoothed
a <- params$text$"reference gdp"
b <- params$text$"reference gfr" 
c <- params$text$"reference sba"

if (nrow(tbl_preds) > 0) {
kableExtra::kbl(tbl_preds,
                row.names = FALSE,
                booktabs = T,
                                align = align_headers,
                escape = FALSE,
                caption = params$text$"table 7 title",
                col.names = kableExtra::linebreak(c(
                              paste0(params$text$"table 7 column names 1"),
                              paste0("GDP", kableExtra::footnote_marker_alphabet(1), kableExtra::footnote_marker_symbol(1), "\n", params$text$"table 7 column names 2 denomination"),
                              paste0("GFR", kableExtra::footnote_marker_alphabet(2), "\n ", params$text$"table 7 column names 3 denomination"),
                              paste0("SBA", kableExtra::footnote_marker_alphabet(3), "\n ", params$text$"table 7 column names 4 denomination")
                ),
                align = align_headers),
                longtable = T) %>%
  kableExtra::kable_styling() %>%
  kableExtra::kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 7) %>%
  kableExtra::footnote(symbol = c(star), alphabet = c(a,b,c), escape = FALSE, threeparttable = T)
}
```
`r if(nrow(tbl_preds) == 0 & lang == "English"){"No data available"}`
`r if(nrow(tbl_preds) == 0 & lang == "Spanish"){"Datos no disponibles"}`
`r if(nrow(tbl_preds) == 0 & lang == "French"){"Pas de données disponibles"}`

<!-- page 7 plot -->
\newpage
# `r params$text$"section plot title"`
`r params$text$"Plot caption"`

```{r echo=FALSE ,message=FALSE, warning=FALSE, fig.width=11,fig.height=3.75}
# fig.height = 4, fig.width = 8 #can be added to r chunk to change size of plot
# Please note that PM is preferred over MMR and the described calculations were conducted using maternal deaths derived from the PM when possible.
# devtools::load_all()
bmat:::plot_bmat_onecountry(
  round_name =  round_name_profile,
  iso_alpha_3_code = iso_alpha_3_code,
  estimates_to_compare = NULL, #readRDS(here::here("test/la1_estimates.rds"))
  year_range = c(min(table1_years), max(table1_years))
)
```

\newpage

```{r echo=FALSE ,message=FALSE, warning=FALSE}
#  determining if this is a country with crisis years, code below on runs if country has crisis
has_crisis <- length(meta$crisis_years.c[[1]]) > 0 & any(meta$crisis_years.c[[1]] > 2000)
```


```{r conditional_block, echo=FALSE, results='asis', eval=has_crisis}
cat("#" , params$text$"table crisis title")
```

```{r conditional_block2, echo=FALSE, results='asis', eval=has_crisis}
cat(params$text$"section crisis notes")
```

```{r conditional_block3, echo=FALSE ,message=FALSE, warning=FALSE, eval=has_crisis}
if (has_crisis) {
  crisis_years <-meta$crisis_years.c[[1]]
  matrix <- matrix_ct_to_df(matrix = meta$crisisdeaths.ct, C = meta$C, value_name = "value")
  isos <- meta$iso.c
  yearst <- meta$year.t
  iso_df <- data.frame(c = 1:length(isos), iso_alpha_3_code = isos)
  years_df <- data.frame(t = 1:length(yearst), year = yearst)
  value_df <- matrix %>%
    dplyr::left_join(years_df, by = c("t")) %>%
    dplyr::left_join(iso_df, by = c("c")) %>%
    dplyr::mutate(iso_alpha_3_code = as.character(iso_alpha_3_code))
  value_df <- value_df %>%
    dplyr::select(year, value) %>%
    dplyr::filter(value > 0) %>%
    dplyr::filter(year %in% crisis_years) %>%
    dplyr::mutate(value = round(value))
  a <- params$text$"reference mortality"
  kableExtra::kbl(value_df,
                  booktabs = T,
                                  align = align_headers,
                  caption = params$text$"table crisis title",
                  col.names = kableExtra::linebreak(c(
                                params$text$"table crisis column 1",
                                paste0(params$text$"table crisis column 2", kableExtra::footnote_marker_alphabet(1), "\n ", params$text$"table crisis column 2 denominator") #replace denominator with paste(\n, text$variable)
                  ),
                  align = align_headers),
                  escape = FALSE,
                  row.names = FALSE,
                  longtable = T) %>%
    kableExtra::kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>%
    kableExtra::footnote(alphabet = c(a), escape = FALSE, threeparttable = T) %>%
  kableExtra::column_spec(1:2, width = "2in") 
}
```
